---
title: "lab5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab05)
```

# Discription

Using api I have build an app which will take input from user and will return us qr code for the specific entry from user.for shinny app it is intracrtion between user and web with the help of Ui and server we can build our app.




# fetch_qr 
there's only one function for main file rest for app which is ui and server 
and last one is for my app.
This code generate qr code for any given name.
we can give length of specific size for qr length.
it has two arguments one is any character from user and other is size of qr we want to get.

```{r }
fetch_qr("lab05",200*200)
```

Shinny App

with the help of api we are trying to generate Qr code one simply can writen anything to get qr code.

```{r }

ui <- function(){
  shiny::fluidPage(
    shiny::textAreaInput("user_input", "Enter your text", value = "defual" ),
    shiny::plotOutput("qr_code", width = "100%", height = "400px"),
  )
}


server <-  function(input, output) {

  reactive({
    input$userinput
  })

  output$qr_code <- shiny::renderPlot({
    qr_data <- (lab05::fetch_qr(input$user_input, size = 150*150))
    a <-  png::readPNG(qr_data, native = FALSE, info = FALSE)
    b <-  matrix(a, nrow=150, byrow = TRUE)

    stats::heatmap(b, Rowv = NA,
            Colv = NA, scale = "none", col = c("black", "white"),
            labRow = "", labCol = "")

  })


}

myap <- function(){
  shiny::shinyApp(ui, server)

}
```

when we run this we will get binary representation of qr here but with the help of api we can generate it.
When you click on run app You will see a page where there will be a letter defual and in box if u write anything it will shown up in the form of Qr code.

we can get qr code of any character or word from this app.
this app happen with the help of a api well call a api whichh convert oiur character into qr with the help of qr fatch and we can make 100000 request in one minute on respective api.

